---
title: "Day 1 mini-project"
author: "By Anonymous Analyst Extraordinaire"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: united
---

```{r}

# INSTRUCTIONS

# You are a seasoned data scientist who has just arrived in Boston. You're looking to go see the sights, but you don't know where they are! Instead of buying a tourist guide like a Muggle, you are going to use your skills in exploratory data analysis and visualization to identify some of the cool spots to visit. 

# Working with your partner, conduct analyses to identify at least THREE cool spots that you want to check out. Use the dashboard format to communicate your findings. You can check e.g. on Google to confirm your findings, but you should include clear commentary indicating how your analysis supports your findings. I've included some of the code from the script we worked on together to help you get started. 

```

```{r}
# You may find the following resources useful: 
# - Your team member(s)! 
# - Data wrangling [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf), 
# - `R` graphics [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf), 
# - [`R` Graphics Cookbook](http://www.cookbook-r.com/Graphs/)
# - [RMarkdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)
```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
```

```{r data_prep}
# put your data preparation code here. To get you started, the data preparation we performed in the session previously has already been pasted in. Feel free to add any additional data preparation code needed for your visualizations

listings <- read_csv('../../data/listings.csv')
calendar <- read_csv('../../data/calendar.csv')

source("clean_prices.R")
listings <- clean_prices(listings)
calendar <- clean_prices(calendar)
```


  




# A First Tab

Column {data-width=650}
-----------------------------------------------------------------------

### Map of best Airbnb places

```{r box_1}

  listings_reduced <- listings %>% 
  mutate(price_per= price/accommodates)%>%
  filter(price_per <=33.33)  %>% 
  
  group_by(neighbourhood) %>%
  
  summarise(price_per = mean(price_per),mean_rating = mean(review_scores_rating,na.rm = TRUE)) %>%
  
  arrange(desc(mean_rating)) %>%
   slice(c(1:10))

areas <- listings_reduced$neighbourhood


data2 <-listings %>%  
  mutate(price_per= price/accommodates)%>%
   filter(price_per <=33.33)  %>% 
  filter(neighbourhood %in% areas)








library(ggmap)

boston_coords <- c(left   = -71.1289, 
				   bottom = 42.3201, 
				   right  = -71.0189, 
				   top    = 42.3701)

basemap <- get_map(location = boston_coords,
				maptype = 'terrain')

ggmap(basemap) + 
	geom_point(aes(x = longitude, y = latitude), 
			   data = data2, 
			   size = .5)






```

Column {data-width=350}
-----------------------------------------------------------------------

### Distribution of prices

Low budget travellers do not need to fear for the quality of their accomodation : Boston has many areas with excellent ratings and low rents.

```{r box_2}
list2 <-listings %>% 
  mutate(price_per= price/accommodates)%>%
  select(price_per) 
  
quantile(list2$price_per)


```

As we can see, the lowest quantile fees correspond to less than 33.33 a night per person. Let's find out below in which areas they are found. 

### Neighbourhoods

These ten boroughs have the best quality/price ratio in Boston.

```{r box_3}
# Put the code for a supporting visualization here. This visualization should add context and nuance, but expect the main visualization to convey the bulk of your message. 

# This is not a good visualization -- always remember to include titles and legends. Make yours better! 

  
  listings %>% 
  mutate(price_per= price/accommodates)%>%
  filter(price_per <=33.33)  %>% 
  
  group_by(neighbourhood) %>%
  
  summarise(price_per = mean(price_per),mean_rating = mean(review_scores_rating,na.rm = TRUE)) %>%
  
  arrange(desc(mean_rating)) %>%
   slice(c(1:10))
```


# A Second Tab

Column {data-width=650}
-----------------------------------------------------------------------

### Box 1

As you can see in the visualization below, we explored the best neighbourhoods in which to stay
if you would like to see the Boston Marathon. If you fancy a cheaper stay, Jamaica Plain is a lovely
option, however, if you're a wealthy marathon aficionado, Downtown is the place to be!


### Average April Prices by Neighbourhood and Date 

```{r box_4}

tiny_data <- listings %>%
  select(id, property_type, neighbourhood)

april_data <- calendar %>%
  mutate(month = month(date, label = TRUE)) %>%
  filter(month == 'Apr') %>%
  left_join(tiny_data,
            by = c('listing_id' = 'id'))

april_data_sum <- april_data %>%
  group_by(date, neighbourhood) %>%
  summarise(avg_price = mean(price, na.rm = TRUE),
            n = n()) %>%
  filter(n >= 300, avg_price > 200)

april_data_sum %>%
  ggplot() +
  aes(x = date,
      y = avg_price,
      color = neighbourhood) +
  geom_line() +
  labs(title = 'Avg Price Over Time') +
  ylab('Avg Price') +
  xlab('Date')
```



Column {data-width=350}
-----------------------------------------------------------------------

### Box 2

Here is a visualization for all you budget ice fishers out there looking to get in a chilly fishing 
trip out on the Charles this December! This chart displays neighbourhood
and property type combinations that are both plentiful and affordable!

```{r box_5}
dec_data <- calendar %>%
  mutate(month = month(date, label = TRUE)) %>%
  filter(month == 'Dec') %>%
  left_join(tiny_data,
            by = c('listing_id' = 'id'))

dec_data_sum <- dec_data %>%
  group_by(neighbourhood, property_type) %>%
  summarise(avg_price = mean(price, na.rm = TRUE),
            n = n()) %>%
  filter(n >= 200, avg_price < 100)

dec_data_sum %>%
  ggplot() +
  aes(x = neighbourhood,
      y = property_type,
      size = avg_price) +
  coord_flip() +
  geom_point() +
  labs(title = 'Best listing Types and Areas for Budget Ice Fishing') +
  ylab('Neighbourhood') +
  xlab('Property Type')

```

